---
title: "Testing"
author: "Brandon"
date: "3/8/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(Rtsne)

tsnedata <- Rtsne(iris,check_duplicates = FALSE,perplexity = 30)
plotdata <- tsnedata$Y
```

This website is created by Brandonyeo in Rstudio using the default teplate and export to Rshinny.io as partof the example for Rstudio-shiny-Tutorials

Watch the original video here:


Downloadthe sources code here
[My Github Page](https://github.com/brandonyph)


To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=TRUE}
inputPanel(
  selectInput("n_breaks", label = "Size of Points",
              choices = c(1,2,3,4,5,6,7,8,9,10), selected = 3),
  
  sliderInput("bw_adjust", label = "Shape of Points:",
              min = 1, max = 20, value = 1, step = 1)
)

renderPlot({
  ggplot(faithful,aes(x=eruptions,y=waiting))   +geom_jitter(shape=input$bw_adjust, size=as.numeric(input$n_breaks))
})
```


```{r tsne, echo=TRUE}
inputPanel(
  sliderInput("Perplexity", label = "Perplexity:",
              min = 1, max = 45, value = 1, step = 1)
)


renderPlot({
  tsnedata <- Rtsne(iris,check_duplicates = FALSE, perplexity =   input$Perplexity)

  plotdata <- as.data.frame(tsnedata$Y)
  ggplot(plotdata,aes(x=V1,y=V2)) +geom_jitter(aes(colour = iris$Species))
})
```
